Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Add author contributions

\authorcontributions{\textbf{Author Contributions:} \hl{For research articles with several authors, a short paragraph specifying their individual contributions must be provided.}}

>>>>

\authorcontributions{\textbf{Author Contributions:} Peter Bachant conducted the
    experiments and analyzed the data. Both authors contributed equally to the
    writing and editing of the manuscript.}
